% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2015-Present Isaac M. Jordan <IsaacJordan95@gmail.com> https://isaacjordan.me
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{enumitem}

\setdescription{leftmargin=0.2in}

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-1pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
	\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
	\textbf{\large Isaac M. Jordan -- Full-Stack Software Engineer}  &  \url{https://isaacjordan.me} \\
	London, United Kingdom &  \url{https://uk.linkedin.com/in/ijordan} \\
	IsaacJordan95@gmail.com &  \url{https://github.com/isaac-jordan} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Summary}
\begin{description}
	\item\noindent Full-stack software engineer with \textbf{8 years experience} building and operating \textbf{global products} focussed on \textbf{brilliant user experience}. Experienced with refining and optimizing teams to sustainably deliver high-quality software, and shipping features that delight customers.
\end{description}

\resheading{Work Experience}
\begin{itemize}
	\item
	\ressubheading{G-Research}{London, UK}{Software Engineer [C\#, TypeScript, React, Angular, K8s, Kafka, SQL]}{Oct 2021 - July 2024}
	\begin{itemize}
		\resitem{\textbf{Enhanced the mission-critical safety of global trading} by designing and developing real-time rejected trade analysis tooling, with great customer feedback.}
		\resitem{Led a project to unblock new ways of trading by \textbf{reducing the effort to configure new trading connections by 90\%}, through a new connection config DSL and approval process.}
		\resitem{Implemented a widget-based UI framework enabling traders to \textbf{build their own dashboards} of components implemented by other teams, \textbf{reducing the need for bespoke development}.}
		\resitem{\textbf{Improved the team's satisfaction with development processes} by implementing new SDLC practices, such as running regular retrospectives, reducing code review turnaround time, and moving project management to a more flexible kanban model.}
		\resitem{Voluntary member of several working groups, including User Interface, and Observability groups, helping \textbf{establish technical direction and best practices across the company}.}
	\end{itemize}

	\item
	\ressubheading{AWS (Amazon CodeGuru Profiler)}{London, UK}{Software Development Engineer II [TypeScript, React, Kotlin, Java, AWS]}{Sep 2019 - Oct 2021}
	\begin{itemize}
		\resitem{\textbf{Launched a new AWS service with a global team}, and led development of simplified profiling visualisations, onboarding workflows, and new APIs for data correlation across AWS services. Authored the first \href{https://aws.amazon.com/blogs/machine-learning/optimizing-application-performance-with-amazon-codeguru-profiler/}{public blog post}, increasing product visibility.}
		\resitem{\textbf{Owned and optimized} the console front-end, maintaining a high-quality codebase as the service expanded to 5 new AWS regions. Guided new engineers in front-end best practices, personally \textbf{cutting page load times by 50\% and reducing bundle size by 20\%}.}
		\resitem{\textbf{Fostered a culture of continuous improvement} by mentoring other engineers and regularly improving development and ops processes. Introduced follow-the-sun on-call rotas and safer feature launch processes. Implemented reusable infrastructure libraries, \textbf{removing over 10k lines of code}.}
	\end{itemize}

	\item
	\ressubheading{Amazon}{Edinburgh, UK}{Software Development Engineer II / I / Intern [Java, TypeScript, React, AWS]}{Sep 2017 - Sep 2019}
	\begin{itemize}
		\resitem{Launched a new programmatic video advertising program and \textbf{increased ad performance by 10x in 6 months} through rigorous A/B experimentation, \textbf{exceeding our team goal of \$500k sales}.}
		\resitem{\textbf{Enabled small advertisers to get more value from their videos} by integrating my team's video rendering API with the Amazon Stores service. Utilised AWS Lambda, DynamoDB, and S3 to bridge the services, and built new TypeScript/React front-end components for Amazon Stores.}
		\resitem{Internship: \textbf{Created a \href{https://pdfpiw.uspto.gov/.piw?PageNum=0&docid=10297026&IDKey=E3B5AD2132FF&HomeUrl=\%2F\%2Fpatft.uspto.gov\%2Fnetahtml\%2FPTO\%2Fpatimg.htm}{patent-awarded} prototype} application to convert existing video content into personalisable videos in a fast (real-time)
		and automated fashion, using Java and OpenCV.}
	\end{itemize}

	\item
	\ressubheading{TBR Global Chauffeuring}{Glasgow, UK}{Software Developer (Intern, then Part-Time) [C\#, MVC.NET, JavaScript]}{Jun 2015 - May 2016}
	\begin{itemize}
		\resitem{\textbf{Cut manual ingestion time of new airport arrivals by 95\%} by preprocessing data using OpenAddressesUK and Google APIs.}
	\end{itemize}

	\item
	\ressubheading{Chi Squared Innovations}{Remote}{Software Developer (Part-Time) [Python, Django, JavaScript, d3.js]}{Sep 2014 - Jun 2015}

\end{itemize}

\pagebreak

\resheading{Education}
\begin{itemize}
	\item
	\ressubheading{University of Glasgow}{Glasgow, UK}{First Class BSc (Hons) in Computer Science}{2013 - 2017}
	\begin{itemize}
		\resitem{\textbf{Received Third Year Class Prize} - Strong A grades in all Computer Science classes, and many Mathematics classes.}
		\resitem{First Prize at Glasgow University Tech Society Hackathon 2015.}
	\end{itemize}
\end{itemize}

\resheading{Projects}
\begin{itemize}
	\item
		\ressubheading{Evolution Racing Academy}{\url{https://evolutionracing.academy}}
		{Online racing league dedicated to coaching newer drivers}{2023 - Present}
		\begin{itemize}
			\resitem{\textbf{Voluntary lead developer} of web platform powering automated ingestion and tracking of race results, driver statistics, and league standings.}
			\resitem{Currently \textbf{over 500 drivers} registered and 11 seasons of racing.}
			\resitem{\textbf{Built using Remix framework}, React, TypeScript, TailwindCSS, and Prisma ORM.}
			\resitem{\textbf{Continuously deployed via GitHub Actions to Fly.io} where it runs with an embedded SQLite database.}
		\end{itemize}

	\item
		\ressubheading{IsaacJordan.me}{\url{https://isaacjordan.me}}
		{Personal website and blog}{2016 - Present}
		\begin{itemize}
			\resitem{\textbf{Since 2016 I've maintained a personal website} representing my work history, along with an occasional blog containing technical and non-technical articles.}
			\resitem{Updating the tech stack of this website has been a great way to \textbf{experiment with new technologies}.}
			\resitem{Originally developed with Python and Django on AWS Lambda / RDS, now uses Remix framework, React, TypeScript, TailwindCSS, and Sanity CMS.}
		\end{itemize}

	\item
		\ressubheading{OBS Screen Recognition}{\url{https://github.com/isaac-jordan/obs-screen-recognition}}
		{Open Broadcaster Software plugin}{2020}
		\begin{itemize}
			\resitem{\textbf{Developed an OBS plugin for Twitch streamers} to automatically switch scenes in OBS depending on in-game content.}
			\resitem{\textbf{Used within the Hell Let Loose game streaming community} to hide tactically sensitive information from broadcast.}
			\resitem{Built using Python, OpenCV for computer vision, Numpy, and MSS for performant screen grabs.}
		\end{itemize}

	\item
		\ressubheading{Google Maps API .NET}{\url{https://github.com/ericnewton76/gmaps-api-net}}
		{Google Maps API C\# Library}{Jun 2015 - Sept 2015}
		\begin{itemize}
			\resitem{Significant contributor to open source class library.}
			\resitem{Personally \textbf{implemented Places API, and TimeZone API} in the library (credited as 'Sheepzez').}
			\resitem{Helped manage tickets created by API consumers, and decided how issues are tackled.}
		\end{itemize}

\end{itemize}

\resheading{Skills}
\begin{description}
	\item[Languages:]
	JavaScript (8 years), TypeScript (7 years), C\# (4 years), Java (4 years), SQL (4 years), Kotlin (2 years), Python (2 years)
	\item[Front-End Technologies:]
	React (5 years), Angular (3 years), Material UI, Remix, DaisyUI, TailwindCSS, Bootstrap, HTML5, CSS4, jQuery
	\item[Back-End Technologies:]
	Kubernetes (k8s), Kafka, PostgreSQL, Microsoft SQL Server, Docker, NodeJS, Grafana, Prometheus, SQLite, Remix, Prisma ORM, HDFS, Trino, Django, OpenCV
	\item[Platforms:]
	AWS (Lambda, Fargate, DynamoDB, S3, RDS, CloudFormation, CloudWatch, CodePipeline, IAM, SNS, SQS, CDK, etc.), Kubernetes (k8s), Fly.io, GitHub Actions, Jenkins CI/CD
	\item[Miscellaneous:]
	Passionate about crafting high quality UX from both the back-end and front-end. Exceptional troubleshooting and debugging skills. Able to quickly grasp interactions across service boundaries.
\end{description}

\end{document}
